Normalized expressions

### 2021-03-15 analysis/normalized.Rmd
Add total number of sites
Add percentage of sites with only one minimized expression

Some useful numbers:
```{r}
nb_call_sites <- E_cano %>%
  pull(src_ref) %>%
  n_distinct()
```

@@

```{r}
poly %>% filter(n_exprs > 1) %>%
  count(common_minimized,  sort = TRUE) %>%
  mutate(common_minimized = map_chr(common_minimized, show_set)) %>% 
  mutate(percent = round(100 * n / nb_call_sites, 2)) %>% 
  datatable()
```

>>>>

Some useful numbers:
```{r}
nb_call_sites <- E_cano %>%
  pull(src_ref) %>%
  n_distinct()

r("Nb call sites", nb_call_sites)
```

@@

```{r}
poly %>%
  count(common_minimized,  sort = TRUE) %>%
  mutate(common_minimized = map_chr(common_minimized, show_set)) %>% 
  mutate(percent = round(100 * n / nb_call_sites, 2)) %>% 
  datatable()
```

How many sites have only one minimized expression?

```{r}
n_one_mini <- poly %>% filter(n_expers == 1) %>% nrow()

r("Nb One Minimized", n_one_mini)
r("Nb One Minimized Percent", ratio(n_one_mini, nb_call_sites))
```
